Automated Verification and Synthesis of Embedded Systems: Advances and Challenges

### 2017-06-21 paper.tex
changes to section 7

Regarding behavior correctness, many other applications can be tackled, such as the ones related to automatic classification. Amoedo {\it et al.} proposed a modulation classification methodology, which the goal of spectrum sensing for opportunistic transmissions. Given that

\textcolor{red}{Eddie: Acho que esta faltando texto aqui, certo?}
%--------------------------------------
\section{Conclusions}
\label{conclusions}
%--------------------------------------

@@

>>>>

Regarding behavior correctness, many other applications can be tackled, such as the ones related to automatic classification. Amoedo {\it et al.} \cite{amoedo} proposed a modulation classification methodology, with the goal of spectrum sensing for opportunistic transmissions. Besides a correct software implementation, {\it i.e.}, source code, which is already covered by formal methods already available in the literature \cite{esbmc_filter,Cordeiro12,Clarke04}, one may argue if the proposed methodology is able to recognize modulations under some reception condition, such as severe analog interference. This way, it would be interesting to develop a verification module for transmission and reception software, which could be capable of creating inputs related to sampled radio frequency signals under a variety of condition, unifying source code and behavior verification. In addition, that kind of implementation usually employs digital filters with specific parameters, which could also be tackled.

Finally, ML techniques are already being used in the software verification area \cite{mlswverif,nguyen}. For instance, Hamel \cite{mlswverif} proposes to induce a theory, through ML, that fits a test set for a program, in such a way that it implement the respective test set. ML is already being employ in space state reduction, ML technique can be used also for invariant generation

%--------------------------------------
\section{Conclusions}
\label{conclusions}
%--------------------------------------

@@

\bibitem{amoedo}
Amoedo D. A., da Silva J\'unior W. S., de Lima Filho E. A.:
\newblock {\em{Parameter Selection for SVM in Automatic Modulation Classification of Analog and Digital Signals}}. 
\newblock In: International Telecommunications Symposium (ITS), pp. 1-5, 2014.

\bibitem{mlswverif}
L Hamel:
\newblock {\em {On the Use of Machine Learning in Formal Software Verification.}} 
\newblock {Technical Report TR03-294, Dept. of Computer Science and Statistics, University of Rhode Island}, 2003.

\bibitem{nguyen}
L Hamel:
\newblock {\em {The Application of Machine Learning Methods in Software Verification and Validation.}} 
\newblock {University of Texas at Austin, master of science dissertation}, 2010.
